---
title: "Assignment 3, Part 1"
output: html_document
---


__Name:__ Norbaya Durr

__Student ID:__

For each of the exercises below, take advantage of R markdown features.  That is, include the code as a code chunk and have Rstudio embed your answers.  See Exercise 0 for an example


## Exercise 0 (example)
_Provide the name of your current working directory and list the files therein_
```{r}
getwd()
dir()
```

(You would then click on the > arrow in your answer code block to run it before continuing)

## Exercise 1
_Use sum() to determine the sum of numbers from 2000 to 20000.  Provide your code and have Rmarkdown produce the actual sum in your answer._

```{r}


```


## Exercise 2
_In one or two sentences, describe what the above code snippet did._ __Important: this refers to the code snippet in the online web manual, NOT the code for Exercise 1__.  You should always be looking at the lab manual when you answer these questions.


The above snippet added the two numerical values within the parenthesis. The sum denotes to take the sum of the numerical values within the parenthesis. 




## Exercise 3
_Add the contents of a and b together and place the results in a new object.  Examine the result.  Include your code.  Try using both `sum()` and `+`; do you get different results?  If so, why?_




## Exercise 4
_What is the sum of the 5th through 10th element of object b?  Provide your code and the sum._



## Exercise 5
_What is the sum of the 3rd, 8th, and 10th element of b?  For both of these exercises should only need to have "b" in your code once._


## Exercise 6
_When extracting from a 2-dimensional object, which number specifies rows and which specifies columns?_

_What does `m[3,]` do?_

_How can you extract the 3rd, 4th and 5th columns of m together as one object?_

## Exercise 7
_What does the cbind command do?  How about rbind?_

_Create a new object "n" where the first row is a new row of numbers (your choice) and the following rows are the rows from matrix m._

_Want more? (OPTIONAL) do the same but reverse the order of the rows from matrix m._

## Exercise 8

Copy or move your Swirl Notes into the repo, add and commit them.

Enter the file name(s) here:

**Turning in the assignment**

1. Click the Knit button to generate an up-to-date html file of your markdown document.  Check it to make sure you are happy with its content.
2. Add your .Rmd and .html files to the repository and commit the changes.
3. Push the changes

**Preview the html on github**

If you want to confirm that the correct html file was uploaded:

1. Click on the html file on github.
2. Click on the "raw" button (right hand side of the screen)
3. Copy the URL at the top of the next page (URL should start with "raw.")
4. Go to https://htmlpreview.github.io and paste in the link (use the same browser you are using in step 3)


install.packages("usethis")
install.packages("gitcreds")
library("usethis")
library("gitcreds")


